Assigning Confidence to Clustering Algorithms

### 2020-03-10 Royal Mail/.history/ConfidenceBounds_20200309100903.tex
Ran Parameter Sweep

    \begin{enumerate}
        \item Relocation clustering: Uses a particular criterion function and works by comparing the resulting function with members attached in different clusters. \NOTE{This would also allow for the 'no class' option to be considered.} This method works only when the time series data are of equal length.
        \item Agglomerative Hierarchical: Places each object into its own cluster and then merges these into larger clusters by trying to minimise the sum of squares variance. This method falters once clusters are chosen since it is unable to adjust
        \item Fuzzy k-means considers using a fuzzy membership scheme for partitions. By warping it is possible to make these more appropriate for time series data of unequal length, but then the distance metric needs to account for this.
    \end{enumerate}
\end{document}

>>>>

    \begin{enumerate}
        \item Relocation clustering: Uses a particular criterion function and works by comparing the resulting function with members attached in different clusters. \NOTE{This would also allow for the 'no class' option to be considered.} This method works only when the time series data are of equal length.
        \item Agglomerative Hierarchical: Places each object into its own cluster and then merges these into larger clusters by trying to minimise the sum of squares variance. This method falters once clusters are chosen since it is unable to adjust
        \item Fuzzy k-means considers using a fuzzy membership scheme for partitions. By warping it is possible to make these more appropriate for time series data of unequal length, but then the distance metric needs to account for this.
    \end{enumerate}

    \NOTE{The major problem here concerns the metric used to judge the distance between two paths. This is particularly a problem in route clustering as we have to take into account issues of varying traffic conditions etc.}

    The modalities for distance/similarity measures which are proposed are

    \begin{itemize}
        \item Euclidean distance (\NOTE{Obviously if time is not taken into account this is shite})
        \item Cross correlation coefficients (such as Pearson's rank etc.). Can also be a function of time
        \item Short time series distance (STS): In which each time series is considered as a piecewise linear function
        \item Dynamic time warping distance. First align the time series and then use Euclidean distance
        \item KL divergence (\NOTE{I quite like this one if the data sets are somewhat aligned first})
        \item J divergence/Chernoff divergence
    \end{itemize}

\end{document}

### 2020-03-10 Royal Mail/.history/ConfidenceBounds_20200309110212.tex
Ran Parameter Sweep

    \begin{itemize}
        \item Euclidean distance (\NOTE{Obviously if time is not taken into account this is shite})
        \item Cross correlation coefficients (such as Pearson's rank etc.). Can also be a function of time
        \item Short time series distance (STS): In which each time series is considered as a piecewise linear function
        \item Dynamic time warping distance. First align the time series and then use Euclidean distance
        \item KL divergence (\NOTE{I quite like this one if the data sets are somewhat aligned first})
        \item J divergence/Chernoff divergence
    \end{itemize}

@@

>>>>

    \begin{itemize}
        \item Euclidean distance (\NOTE{Obviously if time is not taken into account this is shite})
        \item Cross correlation coefficients (such as Pearson's rank etc.). Can also be a function of time (\NOTE{Can also use these as the metric which considers the confidence of attaching a route to a cluster.})
        \item Short time series distance (STS): In which each time series is considered as a piecewise linear function
        \item Dynamic time warping distance. First align the time series and then use Euclidean distance
        \item KL divergence (\NOTE{I quite like this one if the data sets are somewhat aligned first})
        \item J divergence/Chernoff divergence
    \end{itemize}

@@

    In this study, the authors consider how to cluster gene expression data which contains large amounts of random variation. \NOTE{I anticipate that this would be the same case in the GPS data which will be subject to noise.} Importantly, they are able to assign a statistical significance metric when clustering to improve the reliability of the cluster. Previous work relies on doing this by counting how many times a gene is assigned to the same cluster (\NOTE{seems long}). Other recent work which has used GWN to perturb data assigns a perturbed cluster to the original iff it contains a majority of elements in common with the original cluster. (\NOTE{If there is a way to extract features from the GPS data, we could consider this as a method of evaluation, e.g. if routes passed under the same 10 bridges}).

### 2020-03-10 Royal Mail/.history/ConfidenceBounds_20200309110711.tex
Ran Parameter Sweep

>>>>

    Their dissimilarity metric, known as the 'Munneke metric' is able to take into account dissimilarity based on the magnitude and the pattern of gene expression (\NOTE{Perhaps such a combination of metrics would also be useful in route clustering}). Importantly, however, this metric provides a strong confidence measure of the clustering algorithm as it provides a non-negative real value to measure the dissimilarity between the data and a particular cluster.

### 2020-03-10 Royal Mail/.history/ConfidenceBounds_20200309113818.tex
Ran Parameter Sweep

>>>>

    \section{Correlation based dynamic time warping of multivariate time series}

    In this paper they also develop a similarity metric called correlation based dynamic time warping. This is particularly handy for multivariate time series data which presents some correlation between the variables. Then there is the standard 'our algorithm outperforms others'.

    \section{A distance based time series classification framework}

    In this, they develop a toolkit which contains different methods for time series
